Machine Learning and Mixed Strategy Games

### 2020-12-26 LaTeX/paper.tex
title page electric boogaloo
separate TOC
Update paper.tex

% @Author: UnsignedByte
% @Date:   11:12:32, 08-Dec-2020
% @Last Modified by:   UnsignedByte
% @Last Modified time: 00:56:48, 17-Dec-2020

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {./images/} {../results/} }
\usepackage[%  
    colorlinks=true,
    pdfborder={0 0 0},
    linkcolor=black
]{hyperref}
\title{Machine Learning and Mixed Strategy Games}
\author{
	Edmund Lam \\
	\and
	Avi Patni
}
\begin{document}

\maketitle

\tableofcontents

@@

Despite the successes of these experiments, however, the project definitely was constrained in a number of ways, most of which can be attributed to the lack of time. Simulations take processing power, and processing time; despite using multithreading and math optimization, 5000 generations often took an average of $12$ hours, given that (on average) each test contained $100$ neural networks, each playing around $60$ games, with $40$ rounds each, adding up to a whopping $240,000$ games per generation, including calculating moves for each player each round, and adding score totals, and eventually selecting survivors and reproducing. Naturally, only a limited number of tests were able to be run, and room for later re-testing was limited. Given more time, larger neural networks could be run containing more nodes and hidden layers, a larger population of networks could be used to allow for greater diversity in strategy, and more games could be played each generation. Furthermore, more complicated payoff matrices could be designed, containing more than four moves and maybe even more than three players. These could be more thoroughly human-tested to compare human strategies with those devised by the networks. Data analysis was similarly restricted; more time could allow for exploration of how neural networks fared against human opponents, observations into how exactly the neural networks managed to devise such complex behavior through analyzing weights, and more. All in all, this project, though successful, can still be taken much further than it was in this short period, and much deeper analysis could be performed on the resultant data.

>>>>

% @Author: UnsignedByte
% @Date:   11:12:32, 08-Dec-2020
% @Last Modified by:   UnsignedByte
% @Last Modified time: 13:27:40, 17-Dec-2020

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {./images/} {../results/} }
\usepackage[%  
    colorlinks=true,
    pdfborder={0 0 0},
    linkcolor=black
]{hyperref}
\title{Machine Learning and Mixed Strategy Games}
\author{Edmund Lam \and Avi Patni}
\begin{document}
\begin{titlepage}
	\maketitle
	\thispagestyle{empty}
\end{titlepage}
\newpage
  \tableofcontents
\newpage

@@

Despite the successes of these experiments, however, the project definitely was constrained in a number of ways, most of which can be attributed to the lack of time. Simulations take processing power, and processing time; despite using multithreading and math optimization, 5000 generations often took an average of $12$ hours, given that (on average) each test contained $100$ neural networks, each playing around $60$ games, with $40$ rounds each, adding up to a whopping $100\cdot60\cdot40=240,000$ games per generation, including calculating moves for each player each round, and adding score totals, and eventually selecting survivors and reproducing. Naturally, only a limited number of tests were able to be run, and room for later re-testing was limited. Given more time, larger neural networks could be run containing more nodes and hidden layers, a larger population of networks could be used to allow for greater diversity in strategy, and more games could be played each generation. Furthermore, more complicated payoff matrices could be designed, containing more than four moves and maybe even more than three players. These could be more thoroughly human-tested to compare human strategies with those devised by the networks. Data analysis was similarly restricted; more time could allow for exploration of how neural networks fared against human opponents, observations into how exactly the neural networks managed to devise such complex behavior through analyzing weights, and more. All in all, this project, though successful, can still be taken much further than it was in this short period, and much deeper analysis could be performed on the resultant data.
